An open reproducible framework for the study of the iterated prisoner's dilemma

### 2015-12-19 tex/paper.tex
full tournament and Lookerup

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.8\textwidth]{../img/stewart_tournament.pdf}
    \caption{The results from a simple tournament.}
    \label{fig:stewart_tournament}
\end{figure}

@@

>>>>

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.8\textwidth]{../img/stewart_tournament.pdf}
    \caption{The results from \cite{Stewart2012}.}
    \label{fig:stewart_tournament}
\end{figure}

@@

In parallel to the Python library, a tournament is being kept up to date that
pits all strategies against each other. Figure \ref{fig:tournament} shows the
results from the full tournament.

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.8\textwidth]{../img/tournament.pdf}
    \caption{Results from the library tournament (2015-12-19)}
    \label{fig:tournament}
\end{figure}

The current winning strategy is a novel strategy of type: \textbf{LookerUp}. This
is a strategy that maps a given set of states to actions. The state space is
defined generically by \(m, n\) so as to map states to actions in the following
way:

\[(\underbrace{(C, D, D, D, C, D, D, C)}_{m\text{ first actions by opponent}},
\overbrace{((C, C), (C, C))}^{n\text{ last pairs of actions}}) \to D\]

The above example is an incomplete illustration of the mapping for \(m=8, n=2\).
Intuitively this state space uses the initial plays of the opponent to gain some
information about the intentions of it whilst still taking in to account the
recent play.  The actual winning strategy an instance of the this framework for
\(m=n=2\) for which an evolutionary algorithm has been used to train it. More
details of this can be found in \cite{mojones}.
